\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=1.1cm,bottom=1.1cm,left=1.4cm,right=1.4cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{array}
\usepackage{fontawesome5}

\definecolor{accent}{HTML}{2E3440}
\definecolor{muted}{HTML}{6B7280}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}

\titleformat{\section}
  {\color{accent}\normalsize\bfseries}
  {}{0pt}{\MakeUppercase}[\vspace{-4pt}\color{accent}\hrulefill]
\titlespacing*{\section}{0pt}{4pt}{1pt}

% In-column section header (for use inside minipages where \section* layout breaks)
\newcommand{\colsection}[1]{%
  \par\vspace{2pt}%
  {\color{accent}\normalsize\bfseries\MakeUppercase{#1}}\par\nobreak
  \vspace{-3pt}\noindent\textcolor{accent}{\rule{\linewidth}{0.4pt}}\par\vspace{2pt}%
}

\setlist[itemize]{leftmargin=1.1em,itemsep=0pt,topsep=1pt,parsep=0pt}

\newcommand{\role}[4]{%
  \par\vspace{2pt}%
  \noindent\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} \textit{\textcolor{muted}{#2}} & \textcolor{muted}{#3} \\
  \end{tabular*}\par\nobreak
  \vspace{1pt}#4\par
}

\newcommand{\edu}[3]{%
  \par\vspace{1pt}%
  \noindent\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} \textit{\textcolor{muted}{#2}} & \textcolor{muted}{#3} \\
  \end{tabular*}\par
}

\newcommand{\project}[4]{%
  \par\vspace{2pt}%
  \noindent\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} \textcolor{muted}{--- #2} & \href{https://#3}{\textcolor{muted}{#3}} \\
  \end{tabular*}\par\nobreak
  #4\par
}

\newcommand{\contact}[2]{\textcolor{muted}{#1}~\,#2}

\begin{document}

%----- Header: name/title (left) | contact grid (right) -----
\noindent
\begin{minipage}[b]{0.55\linewidth}
  {\Huge\bfseries André Brandão}\\[3pt]
  {\color{muted}\normalsize Platform \& Backend Engineer}
\end{minipage}%
\hfill
\begin{minipage}[b]{0.42\linewidth}
  \small
  \setlength{\tabcolsep}{4pt}
  \renewcommand{\arraystretch}{1.15}
  \begin{tabular}{@{}l@{\hspace{12pt}}l@{}}
    \contact{\faEnvelope}{\href{mailto:eu@andrebrandao.dev}{eu@andrebrandao.dev}} &
      \contact{\faGithub}{\href{https://github.com/andre-brandao}{github.com/andre-brandao}} \\
    \contact{\faGlobe}{\href{https://andrebrandao.dev}{andrebrandao.dev}} &
      \contact{\faMapMarker*}{Belo Horizonte, Brazil} \\
  \end{tabular}
\end{minipage}

\vspace{6pt}

%----- Profile | Skills (side by side) -----
\noindent
\begin{minipage}[t]{0.46\linewidth}
  \colsection{Profile}
  Platform and backend engineer who ships end-to-end, from AWS and Terraform at
  work to a declarative NixOS + Proxmox homelab at home. Currently ML Engineer
  Intern at A3Data, building observability for multi-agent AI systems on Amazon
  Bedrock AgentCore and maintaining the internal Backstage platform. Co-founded
  Crossgeo, shipping production systems for logistics and distribution on AWS.
  Finishing a B.Sc.\ in Computer Science at PUC-MG in 2026.
\end{minipage}%
\hfill
\begin{minipage}[t]{0.52\linewidth}
  \colsection{Skills}
  \small
  \begin{tabular}{@{}p{0.28\linewidth}p{0.68\linewidth}@{}}
    \textbf{Languages} & TypeScript, Python, Go, C, Java, Rust, Bash \\
    \textbf{Backend} & REST / gRPC APIs, microservices, event-driven
      (SQS / EventBridge / DynamoDB Streams), ECS, Lambda, RDS, DynamoDB, S3, CloudFront \\
    \textbf{Infra} & AWS, Cloudflare, Terraform, Pulumi/SST, Backstage,
      K8s (Talos/Rancher), Docker, Proxmox, GitHub Actions, Vault, IAM \\
    \textbf{Data} & PostgreSQL, SQLite, Redis, SQL, NoSQL, Airflow, Spark \\
    \textbf{Observability} & OpenTelemetry, Prometheus / Grafana, distributed tracing \\
    \textbf{AI \& LLMs} & Amazon (Bedrock/AgentCore), multi-agent systems, MCPs, Langchain \\
    \textbf{Tooling} & Linux, Nix / NixOS, Git, SOPS, FluxCD \\
  \end{tabular}
\end{minipage}

\section*{Experience}
\role{ML Engineer Intern}{A3Data --- Belo Horizonte, Brazil}{03/2025 -- Present}{
  \begin{itemize}
    \item Implemented the observability layer for Grupo Elfa's multi-agent
          quotation system on Amazon Bedrock AgentCore, the first AgentCore
          production deployment in Latin America. Added distributed tracing,
          business KPIs and dashboards via OpenTelemetry for a pipeline that
          processes 800k+ quotations per month. Featured in the AWS Brasil
          engineering blog:
          \href{https://aws.amazon.com/pt/blogs/aws-brasil/grupo-elfa-aplicando-amazon-bedrock-agentcore-para-observabilidade-de-sistema-multiagente-em-escala/}{\textit{Grupo Elfa --- Amazon Bedrock AgentCore for multi-agent observability at scale}}.
    \item Built the internal developer platform on Backstage (Spotify) with a
          template engine that covers WhatsApp agents, web LLM agents, ETL
          pipelines (Airflow + Spark) and ML Python projects. Every template
          ships with Terraform infra, deploy pipelines, monitoring and IAM wired
          to company conventions.
    \item Provisioned and deployed production agents and services across AWS ECS,
          Lambda, DynamoDB (incl.\ Streams) and RDS entirely via Terraform.
    \item \textit{Stack:} Python, Terraform, Backstage, OpenTelemetry, Airflow, Spark, AWS.
  \end{itemize}
}
\role{Full Stack Developer, Co-founder}{Crossgeo --- Belo Horizonte, Brazil}{06/2024 -- Present}{
  \begin{itemize}
    \item \textbf{Duarte Distribuidora:} management system in production at a beverage
          distributor, covering inventory, sales, customers and suppliers.
          Svelte, TypeScript, SQLite.
    \item \textbf{Rota 88 Delivery:} last-mile delivery platform in production.
          Ingests orders from iFood and SAIPOS through Lambda webhooks, runs the
          operator web app on ECS with WebSockets for live dispatch, and ships a
          React Native app for couriers covering accept/reject, proof of delivery
          and hand-off to Google Maps for navigation. Restaurants configure between
          several routing heuristics we built for auto-dispatch.
          Svelte, TypeScript, React Native, PostgreSQL on RDS, AWS (ECS + ALB,
          Lambda, CloudFront).
  \end{itemize}
}
\role{Full Stack Developer}{Crossvirus (PUC-MG startup) --- Belo Horizonte, Brazil}{03/2024 -- 2025}{
  Built an epidemiological monitoring platform (Dengue, COVID-19) used in
  Divinópolis and João Monlevade, and coordinated two PUC-MG interns.
  Astro, Svelte, PostgreSQL.
}

\section*{Projects}
\project{Homelab}{Nix / NixOS, Terraform, Proxmox, SOPS, Talos}{github.com/andre-brandao/nixos}{
  Fully declarative infrastructure covering my workstations (NixOS with home-manager)
  and a Proxmox homelab that runs Gitea, HashiCorp Vault, Prometheus and Grafana, and
  an LLM gateway. Each host is its own NixOS module with a matching Terraform stack
  for Proxmox, and all secrets are encrypted with SOPS.
}

\project{GPUi Shell}{Rust, Wayland, D-Bus, IPC, Nix}{github.com/andre-brandao/gpui-shell}{
  A GPU-accelerated Wayland desktop shell written in Rust on top of Zed's GPUI
  framework. It replaces waybar, rofi and swaync with a single app that handles the
  status bar, application launcher, control center and media controls, and works with
  both Hyprland and Niri.
}

\section*{Certifications}
AWS Partner --- Agentic AI Essentials \textbullet{} Generative AI (Technical) \textbullet{}
Digital Sovereignty on AWS (Technical) \textbullet{}
AWS Academy Graduate --- Cloud Foundations.

\section*{Education}
\edu{B.Sc.\ in Computer Science}{PUC-MG, Belo Horizonte, Brazil}{2022 -- 2026/1 (expected)}

\section*{Languages}
\begin{tabular}{@{}p{0.22\linewidth}p{0.76\linewidth}@{}}
  \textbf{Portuguese} & Native \\
  \textbf{English} & Professional working proficiency \\
\end{tabular}

\end{document}
